### 2024-05-31 Paper/paper.tex
Updates from Overleaf

  While ownership is certainly relevant, there could be other characteristics correlated with hospital behavior independent of ownership type. Researchers have focused in particular on explaining variation in NFP behavior by the market they exist in (citations). However, I argue that an observable and economically meaningful factor is the composition top-level hospital managers. In large, publicly traded firms, executive characteristics are shown to be correlated with firm performance, indicating that there is more to firm behavior than ownership status (\cite{bertrand2003managing}; \cite{matsa2013female}; \cite{ahern2012changing}). If hospitals differ in how they value monetary profit vs. societal benefit, then ownership status certainly plays a role in these valuations, but the question remains as to whether management also plays an important role. I contribute to our understanding of hospital and NFP behaviors by investigating whether occupational background, specifically clinical training in executives, affects hospital response to pay-for-performance incentives.

@@

  I estimate how the interaction between hospital type and post program enactment affects readmission and mortality rates. Under the assumption that hospitals would have continued to behave similarly in the absence of the programs, and that leadership teams do not change endogenously with the programs, I identify the differential response to pay-for-performance incentives by different hospital types. Among the hospitals in the data, hospitals with clinically trained executives are the minority, and differ on average from other hospitals along various dimensions. Thus, I ultimately employ synthetic difference-in-differences to analyze a group of comparison hospitals with similar characteristics to treatment hospitals.\footnote{I also present results for the full sample, and find qualitatively similar results.}

   While all hospital types decrease readmission rates after the programs are enacted, NFPs with clinically trained executives respond less than both FPs and NFPs without clinically trained executives. That is, NFPs without clinically trained executives respond to incentives more similarly to FPs than other NFPs. Using changes in executive teams, I decompose this effect into signalling (clinical executives signal underlying hospital preferences), or managing (clinical executives manage the hospital differently) effects. I find that the entire difference in response is driven by a managing effect.

@@

    In light of the theoretical predictions, I test empirically whether different hospital types respond to pay-for-performance incentives differently. I present here linear models with a two-way fixed effects specification. Ultimately, I employ synthetic difference-in-differences, which is estimating the same model with weights that more heavily factor similar trending control groups and time periods. However, for clarity, I present the unweighted specification:

@@

     Second, I assume that executive teams are not determined endogenously with the programs. In the main specification, I limit the sample to hospitals with executive teams that do not change their propensity to hire a clinical executive over time. Thus, I rely on this sample selection not being correlated with the program enactment. In supplementary analyses, I leverage executive team changes to disentangle signalling vs. managing effects, which is only identified if leadership changes are uncorrelated with the policies.

     I assess the validity of this assumption in two ways. First, I analyze whether changes in clinically trained executives occur more often in time periods of program enactment. Second, I analyze whether hospitals who end up getting penalized or receiving payments are more likely to make changes in clinical executive members than those who are not. That is, are hospitals that expect to be affected by the programs more likely to hire or fire clinically trained executives? I consider changes in having any clinically trained executive, as well as changes in the number of clinically trained executives. I estimate the following linear equations:

@@

@@

Further, I present coefficient estimates from Equation \ref{eq:clinical} in Table \ref{tab:MD_noMD_readmort_fullsample}, directly comparing NFPs with and without clinical executives for both readmission and mortality rates. Again, these results are very similar to the main results of the paper, with only slightly larger magnitudes. NFPs without a clinical executive respond to the pay-for-performance incentives by decreasing readmission and mortality rates more aggressively than NFPs with clinical executives.

>>>>

  While ownership is certainly relevant, there could be other characteristics correlated with hospital behavior independent of ownership type. Researchers have focused in particular on explaining variation in NFP behavior using variation in the market they exist in (\cite{horwitz2009hospital}). However, I argue that an observable and economically meaningful factor is the composition of top-level hospital managers. In large, publicly traded firms, executive characteristics are shown to be correlated with firm performance, indicating that there is more to firm behavior than ownership status (\cite{bertrand2003managing}; \cite{matsa2013female}; \cite{ahern2012changing}). If hospitals differ in how they value monetary profit vs. societal benefit, then ownership status certainly plays a role in these valuations, but the question remains as to whether management also plays an important role. I contribute to our understanding of hospital and NFP behaviors by investigating whether occupational background, specifically clinical training in executives, affects hospital response to pay-for-performance incentives.

@@

  I estimate how the interaction between hospital type and post program enactment affects readmission and mortality rates. Under the assumption that hospitals would have continued to behave similarly in the absence of the programs, and that leadership teams do not change endogenously with the programs, I identify the differential response to pay-for-performance incentives among hospital types. That is, I define a group of treatment and comparison hospitals, and estimate how outcomes differ between the two groups after the policy changes. I ultimately employ synthetic difference-in-differences to analyze a group of comparison hospitals with similar characteristics to treatment hospitals.\footnote{I also present results for the full sample, and find qualitatively similar results.}

   While all hospital types decrease readmission rates after the programs are enacted, NFPs with clinically trained executives respond less than both FPs and NFPs without clinically trained executives. That is, NFPs without clinically trained executives respond to incentives more similarly to FPs than other NFPs. Leveraging changes in executive teams, I decompose this effect into signalling (clinical executives signal underlying hospital preferences), or managing (clinical executives manage the hospital differently) effects. I find that the entire difference in response is driven by a managing effect.

@@

    In light of the theoretical predictions, I test empirically whether different hospital types respond to pay-for-performance incentives differently. I present here a two-way fixed effects specification, where the key variable is an interaction between a certain hospital type and time periods after program enactments. Ultimately, I employ synthetic difference-in-differences, which is estimating the same model with weights that more heavily factor similar trending control groups and time periods. However, for clarity, I present the unweighted specification:

@@

     Second, I assume that executive teams are not determined endogenously with the programs. In the main specification, I limit the sample to hospitals with executive teams that do not change their propensity to hire a clinical executive over time. Thus, I rely on this sample selection not being correlated with the program enactment. In supplementary analyses, I leverage executive team changes to disentangle signalling vs. managing effects, which is only identified if leadership changes are uncorrelated with the policies. In Appendix \ref{app:changes}, I present various descriptive statistics of executive team changes over time, showing that hiring and firing of MD executives do not change much over time, the rate of clinical executives to total executives remains stable over time, and the distribution of timing of clinical executive changes.

     I assess the validity of the exogenous changes assumption in two ways. First, I analyze whether changes in clinically trained executives occur more often in time periods of program enactment. Second, I analyze whether hospitals who end up getting penalized or receiving payments are more likely to make changes in clinical executive members than those who are not. That is, are hospitals that expect to be affected by the programs more likely to hire or fire clinically trained executives? I consider changes in having any clinically trained executive, as well as changes in the number of clinically trained executives. I estimate the following linear equations:

@@

\section{Executive Team Changes}\label{app:changes}

Here, I present descriptive statistics of executive team changes. In Figure \ref{fig:change_graph}, I show the average rate of MD executives to total executives, the percent of hospitals who fire an MD, and the percent of hospitals who hire an MD. The fraction of MD executives remains stable over time at approximately .22. Similarly, the percent of hospitals who hire an MD over time remains stable at approximately 21\%. There is a small increase in the percent of hospitals who fire an MD in 2011, but even with this increase firing is not common and stable, ranging from 12\% to 13\%.

\begin{figure}[ht!]
    \centering
    \caption{Executive Team Changes Over Time}
    \includegraphics[width=\textwidth]{Objects/change_graph.pdf}
    \label{fig:change_graph}
\end{figure}

Additionally, I present the number of hospitals who change their propensity to hire a clinically trained executive at different times in Table \ref{tab:change_timing}. I break the timing up into pre-2012, 2012, and post-2012. I show the number of hospitals who have MDs in different time combinations. The number of hospitals that only have an MD executive in 2012, but at no other time, is only 6. The majority of hospitals (187) who ever have a clinical executive have one in every time period.

\import{Tables}{change_num_table_2012.tex}

\section{Results By Condition}

\import{Tables}{fp_read_condition_synth.tex}

\import{Tables}{fp_mort_condition_synth.tex}

\import{Tables}{MD_noMD_readmort_condition_synth.tex}

@@

Further, I present coefficient estimates in Table \ref{tab:MD_noMD_readmort_fullsample} directly comparing NFPs with and without clinical executives for both readmission and mortality rates. Again, these results are very similar to the main results of the paper, with only slightly larger magnitudes. NFPs without a clinical executive respond to the pay-for-performance incentives by decreasing readmission and mortality rates more aggressively than NFPs with clinical executives.
